The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-31 Writeup/paper_v3.tex
actually remove conversation that was supposed to be removed earlier
Claire's comments included

\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
%\newcommand{\rachel}[1]{}
\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
%\newcommand{\arun}[1]{}
\newcommand{\claire}[1]{{\textcolor{green}{#1}}}
\def\a{\alpha}
\def\reff@jnl#1{{\rm#1\/}}

@@

\begin{abstract}
Upcoming weak lensing surveys will survey large cosmological volumes
in order to measure the growth of cosmological structure with time and
thereby constrain dark energy.  One major systematic uncertainty in
this process is the calibration of the weak lensing shape distortions,
or shears.  Nearly all upcoming surveys plan to test their shear
estimation algorithms using sophisticated image simulations that
attempt to mimick real data as closely as possible, including
realistic galaxy populations based on high-resolution data from the
Hubble Space Telescope ({\em HST}).  However, the existing datasets
from the {\em HST} cover very small cosmological volumes, such that
cosmic variance could cause the galaxy population represented in them
to be atypical.  This is particularly the case when selecting galaxy
populations in limited redshift slices, which could be dominated by a
single large overdensity or underdensity.  In that case, the
morphology-density relation could cause changes in the local galaxy
populations that would result in incorrect conclusions to be drawn
about the calibration of shear estimates as a function of redshift.
We directly test this scenario using the COSMOS survey, which is the
largest-area {\em HST} survey to date, and show how the
statistical properties of shape (axis ratio or ellipticity) and
morphological parameters such as \sersicn or the bulge-to-total ratio
are influenced by redshift-dependent cosmic variance in this survey. This
study requires a careful distinction between environment effects from
large-scale structure, which we do not wish to include in simulations,
and general trends in the galaxy population with redshift. We conclude
that this effect is large enough to exceed the systematic error budget
in future surveys, but can be mitigated with careful choice of
training dataset and sufficiently large redshift binning. 
\end{abstract}

@@

For the upcoming surveys to achieve their promise, their systematic error budgets must be below their statistical error budgets.
Systematic error budgets for weak lensing surveys typically include
astrophysical effects, such as intrinsic alignments of galaxy shapes
with large scale density fields \citep[e.g.,][]{2014arXiv1407.6990T} and the effect of baryons on the
matter power spectrum \citep[e.g.,][]{2011MNRAS.415.3649V}, as well as observational uncertainties such as
the ability to robustly infer shears from galaxy observed shapes or
photometric redshifts from their observed colors. 
Given the expected sub-per cent errors on upcoming surveys, systematic errors must be reduced from
 their typical level in the current state-of-the-art
 measurements that typically achieve $\sim 5$ per cent statistical
 errors at best
 \citep[e.g.,][]{2010A&A...516A..63S,2013MNRAS.432.2433H,2013ApJ...765...74J,2013MNRAS.432.1544M}.

@@

 Realistic simulations may use samples based on images from the Hubble
 Space Telescope ({\em HST}).
Software packages like
{\sc GalSim}\footnote{\url{https://github.com/GalSim-developers/GalSim}}
\citep{2014arXiv1407.7676R} can generate images of galaxies from the
{\em HST} as they would appear with an additional lensing shear and
viewed by some lower resolution telescope.  Examples of training samples from the {\em HST} include 
the COSMOS survey \citep[used by the GREAT3 challenge,][]{great3} or the
 Ultra Deep Field \citep[UDF, used by][]{2013ApJ...765...74J}.  These
 two examples serve as the extremes in the {\em HST} samples used as
 the basis for image simulation, with COSMOS being shallower but
representing the current widest contiguous area surveyed by the {\em HST}, and the
 latter being extremely deep but narrow.

For a variety of physical reasons, some of which are still not fully
understood, the shape and morphology of
galaxies depends on their local environment
\citep[e.g.,][]{2014arXiv1402.1172C,2014MNRAS.444.2200D}. 
Hence, local overdensities or underdensities
observed in these {\em HST} fields may (given the small size of the field)
cause the properties of the galaxy population in redshift slices to be
atypical depending on the environment in that slice.  This would have
the undesired consequence of including variation in galaxy properties
due to the COSMOS (or other) survey cosmic variance in the simulated galaxy sample in that redshift slice, rather than
only including ensemble effects that would appear in a large cosmological volume, such as true redshift evolution of
galaxy properties.  Our goal is to quantify the degree to which the
morphology-density correlations in COSMOS cause noticeable changes in
the galaxy populations in narrow redshift slices at a level that could
result in difficulty using the sample to derive redshift-dependent
shear calibrations.   Upcoming surveys will study lensing as a function of
redshift and therefore need to simulate galaxy samples at different
redshifts in order to assess the shear calibration at each redshift.

%The structure of the paper is as follows. In \S\ref{S:data}, we briefly describe the COSMOS catalog that we use for our analysis.
The paper is structured as follows: in Sec.~\ref{S:data}, we describe
the data that we use for this study.  In Sec.~\ref{S:methods}, we
describe our methods for deriving the relevant galaxy properties
like environment, morphology, and shape.  
Using these ingredients, we present our results in Sec.~\ref{S:results}
and discuss their implications in Sec.~\ref{S:summary}.
\section{Data}
\label{S:data}
%In this analysis, we consider the COSMOS sample of galaxies. 
The COSMOS survey \citep{COSMOS_overview, COSMOS_generic, COSMOS_Alexie} is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
in the Hubble Space Telescope (HST).  We use the COSMOS survey to
define a parent sample of galaxy images to be used for making image
simulations, following the approach taken to this problem in
\cite{2012MNRAS.420.1518M,great3}.

@@

In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam, the
Canada-French Hawaii Telescope (CFHT) and KPNO/CTIO, yielding many bands
of imaging data from which to determine high-fidelity photometric
redshifts. 
Photometric redshifts were determined by
\cite{COSMOS_Photoz_30band}. The accuracy of photometric redshifts for
$m_\text{F814W}\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z)$; for $m_\text{F814W}\le$ 24, $\sigma_{\Delta z} = 0.012(1+z)$.
The photometric redshift values become noisier beyond $z\sim 1.2$, and
the  fits to the galaxy light profiles are also somewhat noisy once we
go beyond $m_\text{F814W}\sim 23.5$.   
For this reason, we will exclude all galaxies that have F814W
magnitude fainter than 23.5. However, we will use the
$m_\text{F814W}\le 25.2$ sample that was generated for the GREAT3
challenge to estimate the completeness, which is useful when
generating a volume-limited sample (Sec.~\ref{sub:volumelimiting}).
We first use the $z<1$ flux-limited sample to fit parametric redshift
distribution models (Sec.~\ref{sub:overdensities}), and then
restrict ourselves to $z\le1$ sample for all further analysis. 
% ($S/N \sim 50$ {\bf ?} )
% \rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
%   not the older Mobasher ones.  Need to fix citations. Also, we care
%   about the photo-$z$ accuracy beyond 22.5, so it's important to give
%   some information about it to the depth that we actually use.  Finally, I
%   recommend against mentioning the $S/N$ because the calculation is
%   complicated by the correlated noise, so most people use use
%   magnitude instead of $S/N$.}

@@

Once we volume-limit our sample (explained in Sec.~\ref{sub:volumelimiting}), we again compare the histogram to the models.
If there is no qualitative change in the overdensities, we stick with the preliminary decision. If the overdensity values
flip in sign or become too small, then we classify the redshift bin as `neutral'.
%\arun{New:}
The naive Poisson uncertainty of the counts
in each bin is much lesser compared the difference between the actual number of galaxies present
and the number predicted by the models. For this reason, errorbars have been completely ignored.

@@

\begin{figure}
  \centering
   \includegraphics[width=1.0\columnwidth]{hist2d_mag_mi}
   \caption{2D histogram of galaxies in apparent magnitude
     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3, 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
     The green vertical dotted line represents our luminosity cut. } 
   \label{fig:2Dhist}
\end{figure}

@@

Call the flux-limited ($m_\text{F814W} \le 23.5$) sample \s$0$. Our first approach is to generate a volume-limited sample that is
complete up to $z=1$, by applying a cut on luminosity such that only
galaxies instrinsically brighter than a certain threshold (determined
in detail below) is considered. This threshold is set on the
$k$-corrected $I$-band absolute magnitudes ($M_I$) from the COSMOS PSF-matched
photometry catalog.   The joint distribution of $m_\text{F814W}$ and
$M_I$ is shown in Fig.~\ref{fig:2Dhist}. 
Since the parent sample contains fainter galaxies and is quite
complete to $m_\text{F814W}=25.2$, we compare the $M_I$ distribution
of the $m_\text{F814W}=23.5$ sample with flux-limited samples that
have fainter flux limits, to see where the $m_\text{F814W}<23.5$
sample that we want to use for our tests is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}
At $M_I\sim-22.0$, the
$m_\text{F814W}<23.5$ sample is beginning to lose galaxies in the
$0.9<z<1.0$ redshift bin due to the flux limit. However, the $0.85<z<1$
redshift bin was found to be only moderately overdense, so we choose
to disregard this region for the rest of the analysis, and instead
restrict to $z<0.85$, which is advantageous because it allows us to
choose a somewhat fainter intrinsic luminosity limit for the
analysis.  We relax our luminosity cut %to $-20.8$
so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
We impose the cut at $M_I=-20.8$, which gives 95.3 per cent completeness in
the $0.8 < z \le 0.85$ bin (see Fig.~\ref{fig:MIhist}). The resulting
sample, which has 11~169 galaxies, will be called sample \s$1$ in the remainder
of this work.

However, previous studies
\citep[e.g.,][]{2003A&A...401...73W,2005ApJ...622..116G,2006ApJ...647..853W,Faber2007}
have shown that galaxy intrinsic luminosities evolve with
redshift. Thus, we should also let the luminosity cut that we apply to
volume-limit the sample evolve with redshift. 
Unfortunately, the majority of the published work on evolution of the
luminosity function uses $B$ and $V$ band data, and it is not apparent
that the results should be the same in a redder passband like $I$.  
We use the results from \cite{Faber2007} for the evolution of
$B$-band magnitudes from the DEEP2 and COMBO-17 surveys, which is $
\Delta M_B^* \sim -1.23$ mag per unit redshift (with the sign
indicating that galaxies were intrinsically brighter in the past), for a combined sample
of blue and red galaxies. 
Typically, estimates of evolution in the much redder $K$ band are less
than the estimates of evolution in $B$ and $V$ bands. (\rachel{Please
  include a citation for this statement.}) 
Assuming that the evolution is a smooth function of the wavelength,
the evolution in $I$-band should be in between $B$ and $K$ band. 
Therefore, by considering no evolution (a lower limit) as in our \s$1$, and a second
sample \s$2$ constructed using the $B$-band evolution (as an upper
bound on the $I$-band evolution), we can assume that these two samples
bracket reality, which should be somewhere in between.

Thus, \s$2$ is constructed by letting the luminosity cut evolve,
starting from $M_I = -20.8$ (same as in \s$1$) for the $0.8<z\le0.85$
bin.  The cut values for the other bins are defined by allowing $1.23$
magnitudes of evolution to fainter magnitudes as a function of
redshift (evaluated using the bin centers).  Because of the sign of
redshift evolution, \s$2$ includes  more galaxies.

One might wonder why we cannot use the luminosity function in F814W
based on the COSMOS observations to directly determine the luminosity
function for our sample, thus simplifying this exercise.  However,
this turns out to be highly non-trivial for two reasons.  First, the
F814W observations are relatively shallow compared to the deep
ground-based observations used in many other works for determination
of luminosity evolution.  As a result, it is difficult to get a handle
on the faint end of the luminosity function, and the unknown faint-end
slope turns out to be degenerate with the evolution of the typical
luminosity.  Second, the photometric redshift error is a complicating
factor that requires sophisticated techniques to remove.  A derivation
of the $I$-band luminosity evolution is therefore beyond the scope of
this work.

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Finally, we can circumvent the problem of redshift evolution of the
luminosity by imposing cuts on stellar mass instead. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limits.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which
includes COSMOS. They calculated stellar masses using the procedure
and software described by \cite{2009ApJ...700..221K}, using a set of models
with exponentially declining star formation history \citep{2003MNRAS.344.1000B} assuming a
Chabrier IMF \citep{ChabrierIMF}.  (\rachel{What do you mean by a single stellar population?} \arun{I had lifted that term from the paper since I thought it was important to highlight that. 
They consider those stars that have metallicity of that of the sun
formed at redshift $z=5$.} 
% \rachel{No, look more carefully: they used
% that only to estimate completeness.  Their description of the stellar
% mss estimation process says they used a set of BC03
% models.  This would never work for a single population!  I left this
% conversation here to correct this misimpression, but since I
% fixed the text already, please remove this conversation once you've
% read it - there are no further action items.}) 
We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach a $K_s$-band
$5\sigma$ depth of 24.9. 
As for $M_I$, we compare the stellar mass function in the $m_\text{F814W}\le23.5$ sample with that in the $m_\text{F814W}\le25.2$ sample. 
The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
complete in the redshift bin $0.75 \le z< 0.85$ and has 10~341
galaxies in total across all redshifts.
Thus, we construct a third volume-limited sample \s$3$ by imposing the
stellar mass cut mentioned above.

The number of galaxies in redshift slices
are tabulated in Table~\ref{table:GalaxyCounts} for all three ways
discussed in this section for obtaining a volume-limited sample. The
stellar-mass limited sample is the smallest, most likely because when
converting from flux to stellar mass, the stellar mass-to-light ratios
vary strongly with galaxy type, so red galaxies with high $M_*/L$
simply have too low a flux compared to the blue galaxies at the same
$M_*$, and are not observed.

@@

\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{SMF}
 \caption{Stellar mass distribution for various flux-limited samples
   are shown in three redshift ranges as separate panels. The redshift
   bins have been chosen to facilitate the comparison with  
          a study of the SMF in \protect\cite{Tomczak_SMF}. At high mass, the
          distributions are the same for various flux limits,
          indicating that the samples are complete in that mass
          range. The curves begin to deviate at low masses due to
          incompleteness coming from the flux limit.  The point at
          which the deviation exceeds our threshold determines where the mass cutoff should be to volume-limit the sample.}
 \label{fig:smf}
\end{figure*}

@@

The functional forms for the (flux-limited) redshift distribution that
we used in Sec.~\ref{sub:overdensities} are not well-motivated for a
volume-limited sample. If we fit them to the 
redshift distribution of the volume-limited sample ($M_I < -22$) that doesn't take into account the evolution of the luminosity function,
%\rachel{without or with evolution correction?}\arun{without} 
then due to the absence of an exponential tail in the histogram, the
parameters that set the scale for the redshift ($z_1$ and $z_2$)
become very large.  As a result, both  $p_1(z)$ and $p_2(z)$ defined
in Eqs.~\eqref{E:pz1} and~\eqref{E:pz2} essentially become the same power law.
The best-fitting exponent is remarkably close to $2$ ($a=2.78\pm
0.28$, giving an exponent $1.78\pm 0.28$), suggesting that the
comoving number density of galaxies is constant with redshift as we
would expect for a volume-limited sample in a redshift range for which
evolution is negligible. 
Fig.~\ref{fig:redshift_vollimited} shows that when we do
this, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
increase and are within the $[-0.1, 0.1]$ range that we have defined
as neutral. This is the reason that in Sec.~\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
We will see in Sec.~\ref{S:results} that they are more similar to overdense regions as opposed to underdense regions.
The other redshift slices seem to exhibit a consistent behavior in
Fig.~\ref{fig:redshift_vollimited} as in Fig.~\ref{fig:redshift_fluxlimited}.

@@

For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
Points with unfilled centers and thicker errorbars correspond to the \s$3$ sample and points with filled centers and thinner errorbars correspond to the luminosity-selected samples (\s$1$ or \s$2$).

>>>>

\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
%\newcommand{\rachel}[1]{}
\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
%\newcommand{\arun}[1]{}
\newcommand{\claire}[1]{{\textcolor{magenta}{#1}}}
\def\a{\alpha}
\def\reff@jnl#1{{\rm#1\/}}

@@

\begin{abstract}
Upcoming weak lensing surveys will survey large cosmological volumes
in order to measure the growth of cosmological structure with time and
thereby constrain dark energy.  One major systematic uncertainty in
this process is the calibration of the weak lensing shape distortions,
or shears.  Nearly all upcoming surveys plan to test their shear
estimation algorithms using sophisticated image simulations that
attempt to mimick real data as closely as possible, including
realistic galaxy populations based on high-resolution data from the
Hubble Space Telescope ({\em HST}).  However, the existing datasets
from the {\em HST} cover very small cosmological volumes, such that
cosmic variance could cause the galaxy population in them
to be atypical.  This is particularly the case when selecting galaxy
populations in limited redshift slices, which could be dominated by a
single large overdensity or underdensity.  In that case, the
morphology-density relation could cause changes in the local galaxy
populations that would result in incorrect conclusions to be drawn
about the calibration of shear estimates as a function of redshift.
We directly test this scenario using the COSMOS survey, which is the
largest-area {\em HST} survey to date, and show how the
statistical properties of shape (axis ratio or ellipticity) and
morphological parameters such as \sersicn or the bulge-to-total ratio
are influenced by redshift-dependent cosmic variance in this survey. This
study requires a careful distinction between environment effects from
large-scale structure, which we do not wish to include in simulations,
and general trends in the galaxy population with redshift. We conclude
that this effect is large enough to exceed the systematic error budget
in future surveys, but can be mitigated with careful choice of
training dataset and sufficiently large redshift binning. 
\end{abstract}

@@

For the upcoming surveys to achieve their promise, their systematic error budgets must be below their statistical error budgets.
Systematic error budgets for weak lensing surveys typically include
astrophysical effects, such as intrinsic alignments of galaxy shapes
with large scale density fields \citep[e.g.,][]{2014arXiv1407.6990T} and the effect of baryons on the
matter power spectrum \citep[e.g.,][]{2011MNRAS.415.3649V}, as well as observational uncertainties such as
the ability to robustly infer shears from galaxy observed\claire{strike} shapes or
photometric redshifts from their observed\claire{strike} colors. 
Given the expected sub-per cent \claire{statistical} errors on upcoming surveys, systematic errors must be reduced from
 their typical level in the current state-of-the-art
 measurements that typically achieve $\sim 5$ per cent statistical
 errors at best
 \citep[e.g.,][]{2010A&A...516A..63S,2013MNRAS.432.2433H,2013ApJ...765...74J,2013MNRAS.432.1544M}.

@@

 Realistic simulations may use samples based on images from the Hubble
 Space Telescope ({\em HST}).
Software packages like
{\sc GalSim}\footnote{\url{https://github.com/GalSim-developers/GalSim}}
\citep{2014arXiv1407.7676R} can generate images of galaxies from the
{\em HST} as they would appear with an additional lensing shear and
viewed by some lower resolution telescope.  Examples of training samples from the {\em HST} include 
the COSMOS survey \citep[used by the GREAT3 challenge,][]{great3} or the
 Ultra Deep Field \citep[UDF, used by][]{2013ApJ...765...74J}.  These
 two examples serve as the extremes in the {\em HST} samples used as
 the basis for image simulation, with COSMOS being shallower but
representing\claire{strike} the current widest contiguous area surveyed by the {\em HST}, and the
 latter being extremely deep but narrow.

For a variety of physical reasons, some of which are still not fully
understood, the shape and morphology of
galaxies depends on their local environment
\citep[e.g.,][]{2014arXiv1402.1172C,2014MNRAS.444.2200D}. 
Hence, local overdensities or underdensities
observed in these {\em HST} fields may (given the small size of the field)
cause the properties of the galaxy population in redshift slices to be
atypical depending on the environment in that slice.  This would have\claire{has}
the undesired consequence of including variation in galaxy properties
due to the COSMOS (or other) survey cosmic variance in the simulated galaxy sample in that redshift slice, rather than
only including ensemble effects that would appear in a large cosmological volume, such as true redshift evolution of
galaxy properties.  Our goal is to quantify the degree to which the
morphology-density correlations in COSMOS cause noticeable changes in
the galaxy populations in narrow redshift slices at a level that could
result in difficulty using the sample to derive redshift-dependent
shear calibrations.   Upcoming surveys will study lensing as a function of
redshift and therefore need to simulate galaxy samples at different
redshifts in order to assess the shear calibration at each redshift.

%The structure of the paper is as follows. In \S\ref{S:data}, we briefly describe the COSMOS catalog that we use for our analysis.
The paper is structured as follows: in Sec.~\ref{S:data}, we describe
the data that we use for this study.  In Sec.~\ref{S:methods}, we
describe our methods for deriving the relevant galaxy properties
like environment, morphology, and shape.  
Using these ingredients, we present our results in Sec.~\ref{S:results}
and discuss their implications in Sec.~\ref{S:summary}.
\section{Data}
\label{S:data}
%In this analysis, we consider the COSMOS sample of galaxies. 
The COSMOS survey \citep{COSMOS_overview, COSMOS_generic, COSMOS_Alexie} is a flux-limited, narrow deep field survey covering a contiguous area of $1.64 \text{ deg}^2$ of sky, with images taken using the Advanced Camera for Surveys (ACS) Wide Field Channel (WFC)
in the Hubble Space Telescope (HST).  We use the COSMOS survey to
define a parent sample of galaxy images to be used for making image
simulations, following the approach taken to this problem\claire{strike: to this problem} in
\cite{2012MNRAS.420.1518M,great3}.

@@

In addition to the ACS/WFC (F814W) imaging, the COSMOS field has also been imaged by Subaru Suprime-Cam, the
Canada-French Hawaii Telescope (CFHT) and KPNO/CTIO, yielding many bands
of imaging data from which\claire{used} to determine high-fidelity photometric
redshifts. 
Photometric redshifts were determined by
\cite{COSMOS_Photoz_30band}. The accuracy of photometric redshifts for
$m_\text{F814W}\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z)$; for $m_\text{F814W}\le$ 24, $\sigma_{\Delta z} = 0.012(1+z)$.
The photometric redshift values become noisier beyond $z\sim 1.2$, and
the  fits to the galaxy light profiles are also somewhat noisy once we
go beyond $m_\text{F814W}\sim 23.5$.   
For this reason, we will exclude all galaxies that have F814W
magnitude fainter than 23.5. However, we will use the
$m_\text{F814W}\le 25.2$ sample that was generated for the GREAT3
challenge to estimate the completeness, which is useful when
generating a volume-limited sample (Sec.~\ref{sub:volumelimiting}).
We first use the $z<1$ flux-limited sample to fit parametric redshift
distribution models (Sec.~\ref{sub:overdensities}), and then
restrict ourselves to $z\le1$ sample for all further analysis. 
% ($S/N \sim 50$ {\bf ?} )
% \rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
%   not the older Mobasher ones.  Need to fix citations. Also, we care
%   about the photo-$z$ accuracy beyond 22.5, so it's important to give
%   some information about it to the depth that we actually use.  Finally, I
%   recommend against mentioning the $S/N$ because the calculation is
%   complicated by the correlated noise, so most people use use
%   magnitude instead of $S/N$.}

@@

Once we volume-limit our sample (explained in Sec.~\ref{sub:volumelimiting}), we again compare the histogram to the models.
If there is no qualitative change in the overdensities, we stick with the preliminary decision. If the overdensity values
flip in sign or become too small, then we classify the redshift bin as `neutral'.
%\arun{New:}
The naive Poisson uncertainty of the counts
in each bin is much lesser compared\claire{less than} the difference between the actual number of galaxies present
and the number predicted by the models. For this reason, errorbars have been completely ignored.

@@

\begin{figure}
  \centering
   \includegraphics[width=1.0\columnwidth]{hist2d_mag_mi}
   \caption{2D histogram of galaxies in apparent magnitude
     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3, 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
     The green vertical dotted line represents our luminosity cut. 
     (\claire{What are the colors? Number of galaxies? I'm not sure if this figure is necessary given the text on the next page describing the S1 sample. And the cut here doesn't agree with that in figure 3})
     } 
   \label{fig:2Dhist}
\end{figure}

@@

Call the flux-limited ($m_\text{F814W} \le 23.5$) sample \s$0$. Our first approach is to generate a volume-limited sample that is
complete up to $z=1$, by applying a cut on luminosity such that only
galaxies instrinsically brighter than a certain threshold (determined
in detail below) is\claire{are} considered. This threshold is set on the
$k$-corrected $I$-band absolute magnitudes ($M_I$) from the COSMOS PSF-matched
photometry catalog.   The joint distribution of $m_\text{F814W}$ and
$M_I$ is shown in Fig.~\ref{fig:2Dhist}. 
Since the parent sample contains fainter galaxies and is quite
complete to $m_\text{F814W}=25.2$,(\claire{I'm not sure how the parent sample comes into play here}) we compare the $M_I$ distribution
of the $m_\text{F814W}=23.5$ sample with flux-limited samples that
have fainter flux limits, to see where the $m_\text{F814W}<23.5$
sample that we want to use for our tests is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}
At $M_I\sim-22.0$, the
$m_\text{F814W}<23.5$ sample is beginning to lose galaxies in the
$0.9<z<1.0$ redshift bin due to the flux limit. However, the $0.85<z<1$
redshift bin was found to be only moderately overdense, so we choose
to disregard this region for the rest of the analysis, and instead
restrict to $z<0.85$, which is advantageous because it allows us to
choose a somewhat fainter intrinsic luminosity limit for the
analysis.  We relax our luminosity cut %to $-20.8$
so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
We impose the cut at $M_I=-20.8$, which gives 95.3 per cent completeness in
the $0.8 < z \le 0.85$ bin (see Fig.~\ref{fig:MIhist}). The resulting
sample, which has 11~169 galaxies, will be called sample \s$1$ in the remainder
of this work.

However, previous studies
\citep[e.g.,][]{2003A&A...401...73W,2005ApJ...622..116G,2006ApJ...647..853W,Faber2007}
have shown that galaxy intrinsic luminosities evolve with
redshift. Thus, we should also let the luminosity cut that we apply to
volume-limit the sample evolve with redshift. 
Unfortunately, the majority of the published work on evolution of the
luminosity function uses $B$ and $V$ band data, and it is not apparent
that the results should be the same in a redder passband like $I$.  
We use the results from \cite{Faber2007} for the evolution of
$B$-band magnitudes from the DEEP2 and COMBO-17 surveys, which is $
\Delta M_B^* \sim -1.23$ mag per unit redshift (with the sign
indicating that galaxies were intrinsically brighter in the past), for a combined sample
of blue and red galaxies. 
Typically, estimates of evolution in the much redder $K$ band are less
than the estimates of evolution in $B$ and $V$ bands. (\rachel{Please
  include a citation for this statement.}) 
Assuming that the evolution is a smooth function of the wavelength,
the evolution in $I$-band should be in between $B$ and $K$ band. 
Therefore, by considering no evolution (a lower limit) as in our \s$1$, and a second
sample \s$2$ constructed using the $B$-band evolution (as an upper
bound on the $I$-band evolution), we can assume that these two samples
bracket reality, \claire{strike the rest}which should be somewhere in between.

Thus, \s$2$ is constructed by letting the luminosity cut evolve,
starting from $M_I = -20.8$ (same as in \s$1$) for the $0.8<z\le0.85$
bin.  The cut values for the other bins are defined by allowing $1.23$
magnitudes of evolution to fainter magnitudes as a function of
redshift (evaluated using the bin centers).  Because of the sign of
redshift evolution, \s$2$ includes  more galaxies. (\claire{How many?})

One might wonder why we cannot use the luminosity function in F814W
based on the COSMOS observations to directly determine the luminosity
function(\claire{the LF as a function of redshift, right?}) for our sample, thus simplifying this exercise.  However,
this turns out to be highly non-trivial for two reasons.  First, the
F814W observations are relatively shallow compared to the deep
ground-based observations used in many other works for determination
of luminosity evolution.  As a result, it is difficult to get a handle
on the faint end of the luminosity function, and the unknown faint-end
slope turns out to be degenerate with the evolution of the typical
luminosity.  Second, the photometric redshift error is a complicating
factor that requires sophisticated techniques to remove.  A derivation
of the $I$-band luminosity evolution is therefore beyond the scope of
this work.

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Finally, we can circumvent the problem of redshift evolution of the
luminosity by imposing cuts on stellar mass instead. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limits.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which
includes COSMOS. They calculated stellar masses using the procedure
and software described by \cite{2009ApJ...700..221K}, using a set of models
with exponentially declining star formation history \citep{2003MNRAS.344.1000B} assuming a
Chabrier IMF \citep{ChabrierIMF}. 
% \rachel{No, look more carefully: they used
% that only to estimate completeness.  Their description of the stellar
% mss estimation process says they used a set of BC03
% models.  This would never work for a single population!  I left this
% conversation here to correct this misimpression, but since I
% fixed the text already, please remove this conversation once you've
% read it - there are no further action items.}) 
We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach a $K_s$-band
$5\sigma$ depth of 24.9. (\claire{I think that's only true at the low mass end. Overall, your normalizations are different, which leads to the curve offsets. I'm not sure I would show the Tomczak curve since you don't really use it, and explaining the differences isn't so important.
Also, I don't understand what you mean by all the galaxies are plotted in Figure 4. The figure shows the volume density.})
As for $M_I$, we compare the stellar mass function in\claire{of} the $m_\text{F814W}\le23.5$ sample with that in\claire{of} the $m_\text{F814W}\le25.2$ sample. 
The sample with $\log(M/M_\odot) > 10.15$ is $\sim 95$ per cent
complete in the redshift bin $0.75 \le z< 0.85$ and has 10~341
galaxies in total across all redshifts.
Thus, we construct a third volume-limited sample \s$3$ by imposing the
stellar mass cut mentioned above.

The numbers of galaxies in redshift slices
are tabulated in Table~\ref{table:GalaxyCounts} for all three ways
discussed in this section for\claire{of} obtaining a volume-limited sample. The
stellar-mass limited sample is the smallest, most likely because when
converting from flux to stellar mass, the stellar mass-to-light ratios
vary strongly with galaxy type, so red galaxies with high $M_*/L$
simply have too low a flux compared to the blue galaxies at the same
$M_*$, and are not observed.

@@

\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{SMF}
 \caption{Stellar mass distribution for various flux-limited samples
   are shown in three redshift ranges as separate panels. The redshift
   bins have been chosen to facilitate the comparison with  
          a study of the SMF in \protect\cite{Tomczak_SMF}. At high mass, the
          distributions are the same for various flux limits,
          indicating that the samples are complete in that mass
          range. The curves begin to deviate at low masses due to
          incompleteness coming from the flux limit.  The point at
          which the deviation exceeds our threshold determines where the mass cutoff should be to volume-limit the sample.
          (\claire{middle: Why does your mass function go above Tomczak at higher redshift? If you aren't comparing to it directly, maybe just leave it out and do an internal comparison. Would including errors bars make the agreement better?})
          }
 \label{fig:smf}
\end{figure*}

@@

The functional forms for the (flux-limited) redshift distribution that
we used in Sec.~\ref{sub:overdensities} are not well-motivated for a
volume-limited sample. If we fit them to the 
redshift distribution of the volume-limited sample ($M_I < -22$) that doesn't take into account the evolution of the luminosity function,
%\rachel{without or with evolution correction?}\arun{without} 
then due to the absence of an exponential tail in the histogram, the
parameters that set the scale for the redshift ($z_1$ and $z_2$)
become very large.  As a result, both  $p_1(z)$ and $p_2(z)$ defined
in Eqs.~\eqref{E:pz1} and~\eqref{E:pz2} essentially become the same power law.
The best-fitting exponent is remarkably close to $2$ ($a=2.78\pm
0.28$, giving an exponent $1.78\pm 0.28$), suggesting that the
comoving number density of galaxies is constant with redshift as we
would expect for a volume-limited sample in a redshift range for which
evolution is negligible. 
Fig.~\ref{fig:redshift_vollimited} shows that when we do
this\claire{strike:when we do this}, the values of $\delta_{g,\text{1D}}$ for the $z=0.40-0.55$ bin
increase and are within the $[-0.1, 0.1]$ range that we have defined
as neutral. This is the reason that in Sec.~\ref{sub:overdensities} we classified them as neutral as opposed to underdense.
We will see in Sec.~\ref{S:results} that they are more similar to overdense regions as opposed to underdense regions.
The other redshift slices seem to exhibit a consistent behavior in
Fig.~\ref{fig:redshift_vollimited} as in\claire{and} Fig.~\ref{fig:redshift_fluxlimited}.

@@

\claire{Maybe don't use red and green. It's not an uncommon color-blindness.} For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
Points with unfilled centers and thicker errorbars correspond to the \s$3$ sample and points with filled centers and thinner errorbars correspond to the luminosity-selected samples (\s$1$ or \s$2$).
